---
title: "eDNA Journal Scraper"
author: "5734 9863"
date: "2024-07-26"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(lubridate)

#Set working directory to citation_tracking folder
if (requireNamespace("rstudioapi", quietly = TRUE)) {
  setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
} 

#Check working directory
getwd()

```


Directions for downloading citations not available from Web of Science (via Zotero)
Example: Journal - Environmental DNA 
*Method works for any citation able to be imported into Zotero* 
***Example done in Zotero 6.0.37

1.) Find citations to import
Environmental DNA Journal Query Results: https://onlinelibrary.wiley.com/action/doSearch?field1=AllField&text1=noaa&publication%5B%5D=26374943&publication=&Ppub=&AfterMonth=1&AfterYear=2019&BeforeMonth=12&BeforeYear=2024

2.) Click " Export Citation(s) below the "Refine Search" drop down box to bulk export citations of interest
3.) Check the box next to each citation of interest, click "Next"
4.) Select format: "RIS (ProCite, Reference Manager)" - - - Type of import: "Citation file or direct import"
5.) Click "Export"
6.) Import .ris file into Zotero, organize accordingly
7.) Highlight citations to export, right click, choose "Export Items"
8.) Export as Format: "CSV", Character Encoding: Unicode (UTF-8 wihtout BOM) - Note: "Export Notes" was not selected in this example
9.) Proceed with code below


Import data
```{r}

#Import Zotero citations
zotero_export <- read.csv("eDNA_ZoteroExport_July29_2024.csv")

#Import the core list of NOAA Omics Publications needing new citations
all_noaa_omics <- read.csv(file = "All_NOAA_Omics_Publications_as_of_May_28_2024_EXCLUDING Environmental DNA Journal Articles.xls - savedrecs.csv")

```

Edit zotero citations to match core list: all_noaa_omics
```{r}

View(zotero_export)
View(all_noaa_omics)

zotero_export2 <- zotero_export %>%
                      select(-Publisher) %>%
                      rename(Publication.Type = Item.Type,
                             Author.Full.Names = Author,
                             Article.Title = Title,
                             Source.Title = Publication.Title,
                             Author.Keywords = Manual.Tags,
                             Abstract = Abstract.Note,
                             Publisher = Extra,
                             DOI.Link = Url,
                             Date.of.Export = Access.Date,
                             Publication.Date = Date) %>%
                      mutate(Issue = as.character(Issue))

#Merge tables
# Assuming 'Publication.Title' is the common key for merging
all_noaa_omics_complete <- bind_rows(all_noaa_omics, zotero_export2) 

View(all_noaa_omics_complete)

# Get the current date and format it as YYYY-MM-DD
current_date <- Sys.Date()

# Create the filename with the current date
filename <- paste0("All_NOAA_Omics_Publications_", current_date, "_wZotero.csv")

# Write the CSV file
write.csv(all_noaa_omics_complete, file = filename, row.names = FALSE)

```

